Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-02-16 manuscript/appendix.Rmd
updated supporting information
started fixing up SI
#59

---
title: "appendix"
output: 
  pdf_document:
    fig_caption: yes

@@

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("C:/Users/banburymorganr/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/S1.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "Supporting Information Table 1 (S1): ", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(3:4, width = "7cm") 
```

>>>>

---
title: "Supplementary Information: Global patterns of forest autotrophic carbon fluxes"
author: "Rebecca Banbury Morgan, Valentine Herrmann, Norbert Kunert, Ben Bond-Lamberty, Helene C. Muller-Landau, Kristina J. Anderson-Teixeira"
toc: true
toc_depth: 1
output: 
  pdf_document:
    fig_caption: yes

@@

```{r setup, include = FALSE}
# knitr::opts_knit$set(root.dir = 'C:/Users/gyrcbm/Dropbox/Global_Productivity/manuscript/')
knitr::opts_knit$set(root.dir = '/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/Global_Productivity/manuscript/')
```

\newpage
#Table S1. Climate variable definitions and sources
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("climate_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(3:4, width = "7cm") 
```
